Various examples of cdf plots

### 2017-04-18 analysis/plot_cdf_eg.Rmd
Fixed plots in plot_cdf_eg.Rmd so that they render as PNGs.

---
title: "Various examples of cdf plots"
author: "Matthew Stephens"
date: 2015-10-26
---

@@

```{r egcdf, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
plot_mean_cdf(1)
```

@@

```{r mean_cdf, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n","ash.u","ash.hu","truth"),
              pi0filter = TRUE)
```

@@

```{r mean_cdf_nopen, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
names(myColors) <- c("truth","ash.hu.s","ash.n.s","ash.u.s","qvalue",
                     "locfdr","mixfdr.tnull")
colScale <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n.s","ash.u.s","ash.hu.s","truth"),
              pi0filter = TRUE)

@@

```{r egcdf-reduce, fig.height=3, fig.width=6, crop=TRUE, dev='pdf'}
plot_mean_cdf(1,PLOTMETHODS = c("ash.n","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"))
```

@@

```{r mean_cdf-reduce, dev='pdf',fig.height=3, fig.width=6, crop=TRUE}
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"),
              pi0filter = TRUE)
```

@@

```{r mean_cdf_nopen-reduce, fig.height=3, fig.width=6, crop=TRUE, dev='pdf'}
names(myColors) <- c("truth","ash.hu.s","ash.n.s","ash.u.s","qvalue","locfdr",
                     "mixfdr.tnull")
colScale        <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n.s","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"),
              pi0filter = TRUE)
source("../R/set_plot_colors.R")
```

@@

```{r egcdf-reduce-with-npmle, dev='pdf',fig.height=4.5, fig.width=6, crop=TRUE}
run_nplme = function (SEED = 1,PLOTSCENARIOS = c("spiky","near-normal",
                                                 "flat-top","skew","bimodal")) {
  df = data.frame(seed = NULL,scenario = NULL,method = NULL,x = NULL,
                  y = NULL,pi0 = NULL)
  for (SCENARIO in PLOTSCENARIOS) {
    temp = load_example(dsc_shrink,SEED,SCENARIO,"ash.n","../output/dsc-shrink-files/")
    z    = GLmix(temp$input$betahat)
    df   = rbind(df,data.frame(seed = SEED,scenario = SCENARIO,method = "NPMLE",
                               x = z$x,y = cumsum(z$y)/sum(z$y),pi0 = NA))
  }
  return(df)
}

>>>>

---
title: "Various examples of cdf plots"
author: "Matthew Stephens"
date: '2015-10-26'
---

@@

```{r egcdf, fig.height=3, fig.width=9}
# These chunk options were used to create the figure for the paper:
# dev='pdf', fig.height=3, fig.width=9, crop=TRUE
plot_mean_cdf(1)
```

@@

```{r mean_cdf, fig.height=3, fig.width=9}
# These chunk options were used to create the figure for the paper:
# dev='pdf', fig.height=3, fig.width=9, crop=TRUE
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n","ash.u","ash.hu","truth"),
              pi0filter = TRUE)
```

@@

```{r mean_cdf_nopen, fig.height=3, fig.width=9}
# These chunk options were used to create the figure for the paper:
# dev='pdf', fig.height=3, fig.width=9, crop=TRUE
names(myColors) <- c("truth","ash.hu.s","ash.n.s","ash.u.s","qvalue",
                     "locfdr","mixfdr.tnull")
colScale <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n.s","ash.u.s","ash.hu.s","truth"),
              pi0filter = TRUE)

@@

```{r egcdf-reduce, fig.height=3.5, fig.width=7}
# These chunk options were used to create the figure for the paper:
# fig.height=3, fig.width=6, crop=TRUE, dev='pdf'
plot_mean_cdf(1,PLOTMETHODS = c("ash.n","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"))
```

@@

```{r mean_cdf-reduce, fig.height=3.5, fig.width=7}
# These chunk options were used to create the figure for the paper:
# dev='pdf', fig.height=3, fig.width=6, crop=TRUE
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"),
              pi0filter = TRUE)
```

@@

```{r mean_cdf_nopen-reduce, fig.height=3.5, fig.width=7}
# These chunk options were used to create the figure for the paper:
# fig.height=3, fig.width=6, crop=TRUE, dev='pdf'
names(myColors) <- c("truth","ash.hu.s","ash.n.s","ash.u.s","qvalue","locfdr",
                     "mixfdr.tnull")
colScale        <- scale_colour_manual(name = "method",values = myColors)
plot_mean_cdf(1:100,PLOTMETHODS = c("ash.n.s","truth"),
              PLOTSCENARIOS = c("spiky","near-normal","bimodal"),
              pi0filter = TRUE)
source("../R/set_plot_colors.R")
```

@@

```{r egcdf-reduce-with-npmle, fig.height=5.25, fig.width=7}
# These chunk options were used to create the figure for the paper:
# dev='pdf', fig.height=4.5, fig.width=6, crop=TRUE
run_nplme = function (SEED = 1,PLOTSCENARIOS = c("spiky","near-normal",
                                                 "flat-top","skew","bimodal")) {
  df = data.frame(seed = NULL,scenario = NULL,method = NULL,x = NULL,
                  y = NULL,pi0 = NULL)
  for (SCENARIO in PLOTSCENARIOS) {
    temp = load_example(dsc_shrink,SEED,SCENARIO,"ash.n","../output/dsc-shrink-files/")
    z    = GLmix(temp$input$betahat)
    df   = rbind(df,data.frame(seed = SEED,scenario = SCENARIO,method = "NPMLE",
                               x = z$x,y = cumsum(z$y)/sum(z$y),pi0 = NA))
  }
  return(df)
}
